#### 1. Initial GitHub workflow

a. Pat yourselves on the back if you were able to "fork", then "clone" this repo. Maybe massage your brain, too.

b. Re-save this file with your last and first name as well as altering the title of this file.

#### Tips for creating functions

*Use the least possible number of steps. Work line by line, printing out each value as you create the function. Trying to create a function that will solve the whole problem will typically lead to long debugging times because you will not know where you made the mistake.*

#### 2. if-then-else
Create a function `is.a.number()` that takes a single parameter `X` and returns `"Is a number"` if it is a number, `"Is NA"` if it is an `NA` value, and `"I have no clue"` if it is neither a number nor an `NA` value. Use the `is.na()` and `is.numeric()` functions.


```{r}

func_1 <- function(x){
  if(class(x)=="numeric")
    return("Is a number")
  if(class(x)=="NA")
    return("Is NA")
  if(class(x)!="numeric"| class(x) != "NA")
    return("I have no clue")
}

```



#### 3. primes 
Create a function that when inputting a single prime number between 3 and 100, it will output a `TRUE` or `FALSE` in a `message()`. Insert an error message as if somebody were to insert a number less than 3, greater than 100, or a non-numeric character. (*Please don't insert all of the prime numbers between 3 and 100 into the function...*)

```{r}

library(numbers)
func_2 <- function(x){
  if(class(x)!="numeric")
    stop("x must be numeric")
  if((x < 3)|(x > 100))
    stop("x must be greater than 3 or less than 100")
  if(((x>=3)|x<=100)&&isPrime(x)==TRUE)
    message("TRUE")
  if(((x>=3)|x<=100)&&isPrime(x)==FALSE)
    message("FALSE")
}

```


#### 4. ggplot2

a. Using `ggplot2`, create a function that when inputting a single continuous variable, it will print out a histogram. Include arguments to alter the theme, x-variable label, a title, and a `TRUE` or `FALSE` option to create a density plot.

```{r}
func_3a <- function(z,d,...) {
require(ggplot2)
  
if(class(z)!="numeric")
stop("value must be numeric")
  
p <- qplot(z,...)

if(d==TRUE)
  print(p+geom_density())
if(d==FALSE)
  print(p+geom_histogram())
}

```


b. Similarly, create a function that when inputting two continuous variables, it will print a scatterplot. Additionally, in the console, print the mean and variance of the two variables as well as the coefficient value of the specified x-variable.  Include arguments to alter the title and a `TRUE` or `FALSE` option to include a smoothing method of *lm* aka a simple linear model line in/on the scatterplot.

```{r}
func_3b <- function(x,y,d,...) {
require(ggplot2)
  
if(class(x)!="numeric"|class(y)!="numeric")
stop("values must be numeric")

  
p <- qplot(x,y,d...)

if(d==TRUE)
  print(p+stat_smooth())
if(d==FALSE)
  print(p)

mx <- mean(x)
print(mx)
my <- mean(y)
print(my)

vx <- var(x)
print(vx)
vy <- var(y)
print(vy)

}
```



#### 5. Remaining GitHub workflow

a. Now finish off the workflow of submitting your homework by "committing" the changes locally, "pushing" the changes to YOUR online repo, and finally creating a pull request. 

b. Pat yourselves on the back, again.  You deserved it.
